NumPy---Array Programming in Python

### 2020-01-22 body.tex
Switch interoperability/extensibility order

\section*{Extensibility and Interoperability}

@@

What can NumPy do to support the use of its API without blocking innovation?
We believe that having NumPy as a central point of coordination between array
objects can improve interoperability while supporting growth of a larger
surrounding ecosystem of specialized solutions and new tools.  Primarily, there
exist two types of Python array objects: subclasses of NumPy arrays, and arrays
that mimic NumPy arrays but are fundamentally different.

>>>>

\section*{Interoperability and extensibility}

@@

What can NumPy do to support the use of its API without blocking innovation?
We believe that having NumPy as a central point of coordination between array
objects can improve interoperability while supporting growth of a larger
surrounding ecosystem of specialized solutions and new tools.  Primarily, there
exist two types of Python array objects: (1) arrays that mimic NumPy arrays but are
fundamentally different and (2) subclasses of NumPy arrays.
